A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-07-18 papers/paper1/ms.tex
adding descriptions for figures in paper

  % Helpful resource on how to insert and align images
  % https://www.overleaf.com/learn/latex/Inserting_Images
  \begin{figure}[!htb]
    \centering
    \includegraphics[scale=0.8]{Comparison Between TESS and Kepler Amplitudes.png}
    \caption{Relationship between the calculated amplitudes of TESS and Kepler and how close they are to unity}
  \end{figure}
  \FloatBarrier

@@

  \begin{figure}[!htb]
    \centering
    \includegraphics[width=\linewidth]{Amplitude vs. Rotation for Kepler and TESS.png}
    \caption{Comparison between the rotational period vs. amplitude for both TESS and Kepler. The Kepler and TESS averages are approximately 9350 and 130, respectively}
  \end{figure}
  \FloatBarrier

>>>>

  % Helpful resource on how to insert and align images
  % https://www.overleaf.com/learn/latex/Inserting_Images
  \begin{figure}[!htb]
    \centering
    \includegraphics[scale=0.5]{Comparison Between TESS and Kepler Amplitudes.png}
    \caption{Relationship between the calculated amplitudes of TESS and Kepler and how close they are to unity.}
  \end{figure}
  \FloatBarrier

@@

  \begin{figure}[!htb]
    \centering
    \includegraphics[scale=0.42]{Amplitude vs. Rotation for Kepler and TESS.png}
    \caption{Effect size for starspot contrast as seen in modulation amplitude versus period ($P_{\mathrm{rot}}$ [days]). The black points are the locus of spotted stars in the Kepler as measured by for late K dwarfs. The red points are the same stars, but measured with the TESS mission. The blue and green dashed lines represents the average amplitudes for all plotted stars for both Kepler and TESS, approximately 9350 and 130, respectively.}
  \end{figure}
  \FloatBarrier
